The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-18 dit-paper_ieee.tex
closed issue #29

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		A necessary and sufficient condition of feasibility can easily be written
		based on the DBF \cite{baruah1999generalized}

		\begin{theorem}
			\begin{equation}
				\begin{array}{c}
					\{\tau_1, ..., \tau_n\} \: \text{is feasible}  \iff \\
					\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation}
		\end{theorem}

@@

		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
		computation of one modular inversion per $a_i$ value, which is done in linear
		time with the number of tasks. However, to find all DITs
		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
		combination of $a_i$ values, which is exponential in the number of tasks.
		Algorithm~\ref{alg:multiACRP} is not faster in orders of
		complexity as the computation of all DITs still requires an exponential number
		of answers in the number of tasks, but it is nonetheless significantly faster
		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
		sensitive to the number of different $a_i$ values per task, which means tasks
		with deadlines significantly smaller than periods remain practical.

@@

		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		However, the method used in the synchronous case to remove redundancy does not
		apply here. A more general approach is presented in the following section.

@@

To summarize, we first reduced the number of constraints from every possible
interval $[t_1, t_2]$ to the intervals where $t_1$ is an arrival time and
$t_2$ is a deadline in $[t_d, t_d + H]$ if $t_d$ exists, or in
$[O_{max}, O_{max} + 2H]$ otherwise. This set of constraints is a
correct description of the C-Space, but it is not efficient. Redundant
contraints are removed through a linear integer approach.

@@

	In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

>>>>

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		The following necessary and sufficient condition of feasibility
		based on the DBF is given in \cite{baruah1999generalized}:

		\begin{theorem}
			\begin{equation}
				\begin{array}{c}
					\tau \: \text{is feasible}  \iff
					\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
				\end{array}
			\end{equation}
		\end{theorem}

        Indeed, if there exists values of $t_1$ and $t_2$ such that $\dbf{t_1, t_2} > t_2 - t_1$, it means that more than $t_2 - t_1$ unit of computation have to be done in $t_2 - t_1$ unit of time. Therefore the system is unfeasible.

@@

		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
		computation of one modular inversion per $a_i$ value, which is done in linear
		time with the number of tasks. However, to find all DITs
		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
		combination of $a_i$ values, which is exponential in the number of tasks.
		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the computation of all DITs still requires an exponential number
		of answers in the number of tasks, but it is nonetheless significantly faster
		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
		sensitive to the number of different $a_i$ values per task, which means tasks
		with deadlines significantly smaller than periods remain practical.

@@

		The description based on \cite{baruah1999generalized} and presented in Section \ref{sct:cspaceDescr} was general and
		is still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		However, the method used in the synchronous case to remove redundancy does not
		apply here. A more general approach is presented in the following section.

@@

To summarize, we first reduced the number of constraints from every possible
interval $[t_1, t_2]$ to the intervals where $t_1$ is an arrival time and
$t_2$ is a deadline in $[t_d, t_d + H]$ if $t_d$ exists, or in
$[O_{max}, O_{max} + 2H]$ otherwise. This set of constraints is a
correct description of the C-Space, but it is not efficient. Redundant
constraints are removed through a linear integer approach.

@@

	In other words, fig.~\ref{fig:sizeRatio}
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.
